---
title: "Contagious Yawning in Dogs: Re-analysis"
author: Scott Claessens and Patrick Neilands
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
    toc: true
    number_sections: false
    toc_float: true
---

The purpose of this document is to re-analyse the data from seven studies of contagious yawning in dogs. These studies are:

- [Joly-Mascheroni et al. (2008)](https://royalsocietypublishing.org/doi/abs/10.1098/rsbl.2008.0333)
- [Harr et al. (2009)](https://link.springer.com/article/10.1007/s10071-009-0233-0)
- [O’Hara & Reeve (2011)](https://www.sciencedirect.com/science/article/pii/S0003347210004483)
- [Silva et al. (2012)](https://link.springer.com/article/10.1007/s10071-012-0473-2)
- [Madsen & Persson (2013)](https://link.springer.com/article/10.1007/s10071-012-0568-9)
- [Romero et al. (2013)](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0071365)
- [Buttner & Strasser (2014)](https://link.springer.com/article/10.1007/s10071-013-0641-z)

We would like to thank the authors of these studies for kindly sharing their original data with us.

# 0. Setup

```{r echo=FALSE, cache=FALSE, include=FALSE}
options(width = 120)

library(tidyverse)
library(brms)
library(tidybayes)
library(bayesplot)
library(brmstools)
```

Load the data.

```{r}
d <- 
  read.csv('data/yawnReanalysis.csv') %>%
  as_tibble() %>%
  # create dummy variables for re-analysis
  mutate(condition = ifelse(condition == "Control", 0, 1),
         familiar  = ifelse(familiar  == "Unfamiliar", 0, 1))

d
```

Visualise the outcome.

```{r message=F, warning=F}
d %>%
  ggplot(aes(x = numberYawns)) +
  geom_histogram(binwidth = 0.5) +
  labs(x = 'Number of yawns')
```

And split by study.

```{r message=F, warning=F}
d %>%
  ggplot(aes(x = numberYawns)) +
  geom_histogram(binwidth = 0.5) +
  labs(x = 'Number of yawns') +
  facet_wrap(.~study)
```

These look zero-inflated. A zero-inflated Poisson model follows the general form

$$
\begin{eqnarray}
y_i & \sim & \text{ZIPoisson} (p_i, \lambda_i)\\
\text{logit} (p_i) & = & \alpha_p  + \beta_p x_i \\
\text{log} (\lambda_i) & = & \alpha_\lambda + \text{log(offset)} + \beta_\lambda x_i
\end{eqnarray}
$$

where $p_i$ is the zero-inflation probability (so $1 - p_i$ is the probability of the process getting started). $\text{log(offset)}$ is the log of the exposure length, and simple algebra means that $\lambda_i$ is now the expected *rate* per exposure length, rather than the count.

To make sure that assuming zero-inflation is not affecting our results, we will also run these models with a Poisson distribution without zero-inflation.

# 1. Fit zero-inflated Poisson models

## 1.1. Intercept-only model

We utlise a Bayesian multilevel modelling approach here, including random effects for individual dogs nested within studies. Throughout, we use the same linear model to predict $\lambda_i$ (the rate of yawning) and $p_i$ (the probability of the yawning process never even getting started). The latter is called `zi` inside the model formula. 

To begin, we fit an intercept-only model.

```{r eval=F}
m1.1 <- brm(data = d, family = zero_inflated_poisson,
          bf(numberYawns ~ 1 + offset(log(secs)) + (1 | study/ID),
             zi ~ 1 + (1 | study/ID)),
          iter = 2000, warmup = 1000, chains = 4, cores = 4,
          control = list(adapt_delta = 0.99))

m1.1 <- add_ic(m1.1, ic = c("loo","waic"))

save(m1.1, file = 'models/m1.1.rda')
```

```{r echo=F}
load('models/m1.1.rda')
```

```{r}
print(m1.1)
```

Let's interpret each parameter in turn. The zero-inflation parameter `zi` is xxxxx. This is on the logit scale, so we need to calculate the inverse logit.

```{r}
post <- posterior_samples(m1.1)

1 - inv_logit_scaled(post$b_zi_Intercept) %>% # prob of yawning process getting started
  median() %>%
  round(2)
```

The median probability of the yawning process getting started is xxxxxx.

Let's calculate the average yawning rate once the yawning process gets started.

```{r}
(exp(post$b_Intercept) * 60) %>% # yawns per minute
  median() %>%
  round(2)
```

The dogs yawn xxxxx times a minute, on average. Let's split this by study.

```{r}
brmstools::forest(m1, pars = 'Intercept', grouping = 'study')
```

Average yawning rate is lowest in BT et al, but highest in SIL et al.

## 1.2. Condition-only model

Next, we add condition to the model, also as a random effect grouped by individual dogs nested within studies.

```{r eval=F}
m1.2 <- brm(data = d, family = zero_inflated_poisson,
          bf(numberYawns ~ 0 + intercept + condition + offset(log(secs)) + 
               (0 + intercept + condition | study/ID),
             zi ~ 0 + intercept + condition + 
               (0 + intercept + condition | study/ID)),
          prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                    prior(normal(0, 1), class = b, coef = "condition"),
                    prior(logistic(0, 1), class = b, coef = "intercept", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "condition", dpar = zi)),
          iter = 2000, warmup = 1000, chains = 4, cores = 4,
          control = list(adapt_delta = 0.99))

m1.2 <- add_ic(m1.2, ic = c("loo","waic"))

save(m1.2, file = 'models/m1.2.rda')
```

```{r echo=F}
load('models/m1.2.rda')
```

```{r}
print(m1.2)
```

## 1.3. Familiarity-only model

We replace condition with familiarity in the model, again as a random effect grouped by individual dogs nested within studies.

```{r eval=F}
m1.3 <- brm(data = d, family = zero_inflated_poisson,
          bf(numberYawns ~ 0 + intercept + familiar + offset(log(secs)) + 
               (0 + intercept + familiar | study/ID),
             zi ~ 0 + intercept + familiar + 
               (0 + intercept + familiar | study/ID)),
          prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                    prior(normal(0, 1), class = b, coef = "familiar"),
                    prior(logistic(0, 1), class = b, coef = "intercept", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "familiar", dpar = zi)),
          iter = 2000, warmup = 1000, chains = 4, cores = 4,
          control = list(adapt_delta = 0.99))

m1.3 <- add_ic(m1.3, ic = c("loo","waic"))

save(m1.3, file = 'models/m1.3.rda')
```

```{r echo=F}
load('models/m1.3.rda')
```

```{r}
print(m1.3)
```

## 1.4. Condition + Familiarity model

We include both condition and familiarity as additive effects.

```{r eval=F}
m1.4 <- brm(data = d, family = zero_inflated_poisson,
          bf(numberYawns ~ 0 + intercept + condition + familiar + offset(log(secs)) + 
               (0 + intercept + condition + familiar | study/ID),
             zi ~ 0 + intercept + condition + familiar + 
               (0 + intercept + condition + familiar | study/ID)),
          prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                    prior(normal(0, 1), class = b, coef = "condition"),
                    prior(normal(0, 1), class = b, coef = "familiar"),
                    prior(logistic(0, 1), class = b, coef = "intercept", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "condition", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "familiar", dpar = zi)),
          iter = 2000, warmup = 1000, chains = 4, cores = 4,
          control = list(adapt_delta = 0.99))

m1.4 <- add_ic(m1.4, ic = c("loo","waic"))

save(m1.4, file = 'models/m1.4.rda')
```

```{r echo=F}
load('models/m1.4.rda')
```

```{r}
print(m1.4)
```

## 1.5. Interaction model

Finally, we allow condition and familiarity to interaction with one another.

```{r eval=F}
m1.5 <- brm(data = d, family = zero_inflated_poisson,
          bf(numberYawns ~ 0 + intercept + condition*familiar + offset(log(secs)) + 
               (0 + intercept + condition*familiar | study/ID),
             zi ~ 0 + intercept + condition*familiar + 
               (0 + intercept + condition*familiar | study/ID)),
          prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                    prior(normal(0, 1), class = b, coef = "condition"),
                    prior(normal(0, 1), class = b, coef = "familiar"),
                    prior(normal(0, 1), class = b, coef = "condition:familiar"),
                    prior(logistic(0, 1), class = b, coef = "intercept", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "condition", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "familiar", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "condition:familiar", dpar = zi)),
          iter = 2000, warmup = 1000, chains = 4, cores = 4,
          control = list(adapt_delta = 0.99))

m1.5 <- add_ic(m1.5, ic = c("loo","waic"))

save(m1.5, file = 'models/m1.5.rda')
```

```{r echo=F}
load('models/m1.5.rda')
```

```{r}
print(m1.5)
```

## 1.6. Compare models

WAIC.

```{r}
compare_ic(m1.1, m1.2, m1.3, m1.4, m1.5, ic = "waic")
```

LOO.

```{r}
compare_ic(m1.1, m1.2, m1.3, m1.4, m1.5, ic = "loo")
```