---
title: "Contagious Yawning in Dogs: Re-analysis"
author: Scott Claessens and Patrick Neilands
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
    toc: true
    number_sections: false
    toc_float: true
---

The purpose of this document is to re-analyse the data from six studies of contagious yawning in dogs. These studies are:

- [Joly-Mascheroni et al. (2008)](https://royalsocietypublishing.org/doi/abs/10.1098/rsbl.2008.0333)
- [O’Hara & Reeve (2011)](https://www.sciencedirect.com/science/article/pii/S0003347210004483)
- [Silva et al. (2012)](https://link.springer.com/article/10.1007/s10071-012-0473-2)
- [Madsen & Persson (2013)](https://link.springer.com/article/10.1007/s10071-012-0568-9)
- [Romero et al. (2013)](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0071365)
- [Buttner & Strasser (2014)](https://link.springer.com/article/10.1007/s10071-013-0641-z)

We would like to thank the authors of these studies for kindly sharing their original data with us.

# 0. Setup

```{r echo=FALSE, cache=FALSE, include=FALSE}
options(width = 120)

library(tidyverse)
library(brms)
library(tidybayes)
library(bayesplot)
library(brmstools)
library(ggridges)
```

Load the data.

```{r}
d <- 
  read.csv('data/yawnReanalysis.csv') %>%
  as_tibble() %>%
  # create dummy variables for re-analysis
  mutate(condition    = ifelse(condition == "Control", 0, 1),
         familiar     = ifelse(familiar  == "Unfamiliar", 0, 1),
         type         = ifelse(type == "Shelter", 0, 1),
         presentation = ifelse(presentation == "A", 0, 1),
         live         = ifelse(live == "Recording", 0, 1),
         demonstrator = ifelse(demonstrator == "Human", 0, 1))

d
```

Visualise the outcome.

```{r message=F, warning=F, echo=F}
d %>%
  ggplot(aes(x = numberYawns)) +
  geom_histogram(binwidth = 0.5) +
  labs(x = 'Number of yawns')
```

And split by study.

```{r message=F, warning=F, echo=F}
d %>%
  ggplot(aes(x = numberYawns)) +
  geom_histogram(binwidth = 0.5) +
  labs(x = 'Number of yawns') +
  facet_wrap(.~study)
```

These look zero-inflated. A zero-inflated Poisson model follows the general form

$$
\begin{eqnarray}
y_i & \sim & \text{ZIPoisson} (p_i, \lambda_i)\\
\text{logit} (p_i) & = & \alpha_p  + \beta_p x_i \\
\text{log} (\lambda_i) & = & \alpha_\lambda + \text{log(offset)} + \beta_\lambda x_i
\end{eqnarray}
$$

where $p_i$ is the zero-inflation probability (so $1 - p_i$ is the probability of the process getting started). $\text{log(offset)}$ is the log of the exposure length, and simple algebra means that $\lambda_i$ is now the expected *rate* per exposure length, rather than the count.

To ensure that assuming zero-inflation is not affecting our results, we will also run these models with a Poisson distribution without zero-inflation.

# 1. Fit zero-inflated Poisson models

## 1.1. Intercept-only model

We utlise a Bayesian multilevel modelling approach here, including random effects for individual dogs nested within studies. Throughout, we use the same linear model to predict $\lambda_i$ (the rate of yawning) and $p_i$ (the probability of the yawning process never even getting started). The latter is called `zi` inside the model formula.

To begin, we fit an intercept-only model.

```{r echo=F, eval=F}
m1.1 <- brm(data = d, family = zero_inflated_poisson,
          bf(numberYawns ~ 1 + offset(log(secs)) + (1 | study/ID),
             zi ~ 1 + (1 | study/ID)),
          iter = 2000, warmup = 1000, chains = 4, cores = 4,
          control = list(adapt_delta = 0.99))

m1.1 <- add_ic(m1.1, ic = c("loo","waic"))

save(m1.1, file = 'models/m1.1.rda')
```

```{r echo=F}
load('models/m1.1.rda')
summary(m1.1)
```

Let's interpret each parameter in turn. The zero-inflation parameter `zi` is -0.63. This is on the logit scale, so we need to calculate the inverse logit.

```{r}
post <- posterior_samples(m1.1)

1 - inv_logit_scaled(post$b_zi_Intercept) %>% # prob of yawning process getting started
  median() %>%
  round(2)
```

The median probability of the yawning process getting started is 0.65.

Let's calculate the average yawning rate once the yawning process gets started.

```{r}
(exp(post$b_Intercept) * 60) %>% # yawns per minute
  median() %>%
  round(2)
```

The dogs yawn 0.16 times a minute, on average.

## 1.2. Condition-only model

Next, we add condition to the model, also as a random effect grouped by individual dogs nested within studies.

```{r echo=F, eval=F}
m1.2 <- brm(data = d, family = zero_inflated_poisson,
          bf(numberYawns ~ 0 + intercept + condition + offset(log(secs)) + 
               (0 + intercept + condition | study/ID),
             zi ~ 0 + intercept + condition + 
               (0 + intercept + condition | study/ID)),
          prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                    prior(normal(0, 1), class = b, coef = "condition"),
                    prior(logistic(0, 1), class = b, coef = "intercept", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "condition", dpar = zi)),
          iter = 2000, warmup = 1000, chains = 4, cores = 4,
          control = list(adapt_delta = 0.99, max_treedepth = 15))

m1.2 <- add_ic(m1.2, ic = c("loo","waic"))

save(m1.2, file = 'models/m1.2.rda')
```

```{r echo=F}
load('models/m1.2.rda')
summary(m1.2)
```

Get difference between conditions.

```{r}
post <- posterior_samples(m1.2)

# yawning rates (per minute)
cond1 <- exp(post$b_intercept) * 60
median(cond1)

cond2 <- exp(post$b_intercept + post$b_condition) * 60
median(cond2)

diff <- cond2 - cond1

# proportion of prob mass above zero
sum(diff > 0) / 4000
```

Bayes factor for condition parameter.

```{r}
(hyp1.2 <- hypothesis(m1.2, "condition > 0"))
```

Visualise effect of condition.

```{r warning=F, message=F,echo=F}
fig1 <-
  tibble(
    Control  = exp(post$b_intercept) * 60,
    Yawning  = exp(post$b_intercept + post$b_condition) * 60
    ) %>%
  gather(Condition, yawns) %>%
  
  ggplot(aes(x = yawns, fill = Condition, colour = Condition)) +
  geom_density(alpha = 0.1) +
  xlab("Yawns per minute") +
  xlim(c(0,0.6)) +
  theme_classic() +
  theme(axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 10)))

ggsave(fig1, file = "figures/fig1.pdf", width = 5, height = 3)

fig1
```

The effect of condition across studies.

```{r echo=F, message=F, warning=F}
brmstools::forest(m1.2, pars = 'condition', grouping = 'study') +
  geom_vline(xintercept = 0, linetype = "dashed")
```

BT et al. is the only study where the parameter crosses zero, and is also the largest study and the only one done entirely with shelter dogs. We should control for this later.

## 1.3. Familiarity-only model

We replace condition with familiarity in the model, again as a random effect grouped by individual dogs nested within studies.

```{r echo=F, eval=F}
m1.3 <- brm(data = d, family = zero_inflated_poisson,
          bf(numberYawns ~ 0 + intercept + familiar + offset(log(secs)) + 
               (0 + intercept | study/ID),
             zi ~ 0 + intercept + familiar + 
               (0 + intercept | study/ID)),
          prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                    prior(normal(0, 1), class = b, coef = "familiar"),
                    prior(logistic(0, 1), class = b, coef = "intercept", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "familiar", dpar = zi)),
          iter = 2000, warmup = 1000, chains = 4, cores = 4,
          control = list(adapt_delta = 0.99, max_treedepth = 15))

m1.3 <- add_ic(m1.3, ic = c("loo","waic"))

save(m1.3, file = 'models/m1.3.rda')
```

```{r echo=F}
load('models/m1.3.rda')
summary(m1.3)
```

## 1.4. Condition + Familiarity model

We include both condition and familiarity as additive effects.

```{r echo=F, eval=F}
m1.4 <- brm(data = d, family = zero_inflated_poisson,
          bf(numberYawns ~ 0 + intercept + condition + familiar + offset(log(secs)) + 
               (0 + intercept + condition | study/ID),
             zi ~ 0 + intercept + condition + familiar + 
               (0 + intercept + condition | study/ID)),
          prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                    prior(normal(0, 1), class = b, coef = "condition"),
                    prior(normal(0, 1), class = b, coef = "familiar"),
                    prior(logistic(0, 1), class = b, coef = "intercept", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "condition", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "familiar", dpar = zi)),
          iter = 2000, warmup = 1000, chains = 4, cores = 4,
          control = list(adapt_delta = 0.99, max_treedepth = 15))

m1.4 <- add_ic(m1.4, ic = c("loo","waic"))

save(m1.4, file = 'models/m1.4.rda')
```

```{r echo=F}
load('models/m1.4.rda')
summary(m1.4)
```

Get difference between conditions, controlling for familiarity.

```{r}
post <- posterior_samples(m1.4)

# yawning rates (per minute)
cond1 <- exp(post$b_intercept) * 60
median(cond1)

cond2 <- exp(post$b_intercept + post$b_condition) * 60
median(cond2)

diff <- cond2 - cond1

# proportion of prob mass above zero
sum(diff > 0) / 4000
```

Bayes factor for condition parameter.

```{r}
(hyp1.4 <- hypothesis(m1.4, "condition > 0"))
```

## 1.5. Condition*Familiarity model

Finally, we allow condition and familiarity to interact with one another.

```{r echo=F, eval=F}
m1.5 <- brm(data = d, family = zero_inflated_poisson,
          bf(numberYawns ~ 0 + intercept + condition*familiar + offset(log(secs)) + 
               (0 + intercept + condition | study/ID),
             zi ~ 0 + intercept + condition*familiar + 
               (0 + intercept + condition | study/ID)),
          prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                    prior(normal(0, 1), class = b, coef = "condition"),
                    prior(normal(0, 1), class = b, coef = "familiar"),
                    prior(normal(0, 1), class = b, coef = "condition:familiar"),
                    prior(logistic(0, 1), class = b, coef = "intercept", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "condition", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "familiar", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "condition:familiar", dpar = zi)),
          iter = 2000, warmup = 1000, chains = 4, cores = 4,
          control = list(adapt_delta = 0.999, max_treedepth = 15))

m1.5 <- add_ic(m1.5, ic = c("loo","waic"))

save(m1.5, file = 'models/m1.5.rda')
```

```{r echo=F}
load('models/m1.5.rda')
summary(m1.5)
```

Get yawning rate in each cell of 2x2 design.

```{r}
post <- posterior_samples(m1.5)

# yawning rates (per minute)
cond1unfam <- exp(post$b_intercept) * 60
cond2unfam <- exp(post$b_intercept + post$b_condition) * 60
cond1fam   <- exp(post$b_intercept + post$b_familiar) * 60
cond2fam   <- exp(post$b_intercept + post$b_condition + 
                    post$b_familiar + post$`b_condition:familiar`) * 60

median(cond1unfam)
median(cond2unfam)
median(cond1fam)
median(cond2fam)
```

Are there any differences in yawning rate? Get proportions of prob mass above zero for each contrast.

```{r}
diff1 <- cond2fam - cond1unfam
diff2 <- cond2fam - cond2unfam
diff3 <- cond2fam - cond1fam
diff4 <- cond1fam - cond1unfam
diff5 <- cond1fam - cond2unfam
diff6 <- cond2unfam - cond1unfam

sum(diff1 > 0) / 4000
sum(diff2 > 0) / 4000
sum(diff3 > 0) / 4000
sum(diff4 > 0) / 4000
sum(diff5 > 0) / 4000
sum(diff6 > 0) / 4000
```

Does the effect of condition differ between familiar and unfamiliar demonstrators? Interaction effect.

```{r}
sum(diff3 - diff6 > 0) / 4000
```

Visualise.

```{r warning=F, message=F, echo=F}
fig2 <-
  tibble(
    ControlUnfamiliar  = exp(post$b_intercept) * 60,
    YawningUnfamiliar  = exp(post$b_intercept + post$b_condition) * 60,
    ControlFamiliar    = exp(post$b_intercept + post$b_familiar) * 60,
    YawningFamiliar    = exp(post$b_intercept + post$b_condition 
                             + post$b_familiar + post$`b_condition:familiar`) * 60
    ) %>%
  gather(cell, yawns) %>%
  mutate(Condition   = rep(rep(c("Control", "Yawning"), each = 4000), times = 2),
         Familiarity = rep(c("Unfamiliar", "Familiar"), each = 8000)) %>%
  
  ggplot(aes(x = yawns, fill = Condition, colour = Condition)) +
  geom_density(alpha = 0.1) +
  xlab("Yawns per minute") +
  xlim(c(0,0.6)) +
  facet_wrap(.~Familiarity) +
  theme_classic() +
  theme(axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 10)))

ggsave(fig2, file = "figures/fig2.pdf", width = 6, height = 3)

fig2
```

Let's compare all models so far. WAIC.

```{r}
compare_ic(m1.1, m1.2, m1.3, m1.4, m1.5, ic = "waic")
model_weights(m1.1, m1.2, m1.3, m1.4, m1.5, weights = "waic") %>% round(2)
```

LOO.

```{r}
compare_ic(m1.1, m1.2, m1.3, m1.4, m1.5, ic = "loo")
model_weights(m1.1, m1.2, m1.3, m1.4, m1.5, weights = "loo") %>% round(2)
```

The best models are `m1.2`, `m1.4`, and `m1.5` - all the models that have a condition parameter. None of these models are substantially better than one another. This suggests that condition has an effect, but familiarity doesn't interact with it.

Going forward, we choose the condition-only model to continue analysing, as the most parsmionious model. Next, we add controls to see if the effect of condition is robust.

## 1.6. Condition + Type model

We include both condition and type (shelter/pet) as additive effects.

```{r echo=F, eval=F}
m1.6 <- brm(data = d, family = zero_inflated_poisson,
          bf(numberYawns ~ 0 + intercept + condition + type + offset(log(secs)) + 
               (0 + intercept + condition | study/ID),
             zi ~ 0 + intercept + condition + type + 
               (0 + intercept + condition | study/ID)),
          prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                    prior(normal(0, 1), class = b, coef = "condition"),
                    prior(normal(0, 1), class = b, coef = "type"),
                    prior(logistic(0, 1), class = b, coef = "intercept", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "condition", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "type", dpar = zi)),
          iter = 2000, warmup = 1000, chains = 4, cores = 4,
          control = list(adapt_delta = 0.995, max_treedepth = 15))

m1.6 <- add_ic(m1.6, ic = c("loo","waic"))

save(m1.6, file = 'models/m1.6.rda')
```

```{r echo=F}
load('models/m1.6.rda')
summary(m1.6)
```

Effect of condition?

```{r}
post <- posterior_samples(m1.6)
sum(post$b_condition > 0) / 4000
```

Similar to before. Bayes factor?

```{r}
(hyp1.6 <- hypothesis(m1.6, "condition > 0"))
```

Model comparison.

```{r}
compare_ic(m1.2, m1.6, ic = "waic")
compare_ic(m1.2, m1.6, ic = "loo")
```


## 1.7. Condition + Presentation model

```{r echo=F, eval=F}
m1.7 <- brm(data = d, family = zero_inflated_poisson,
          bf(numberYawns ~ 0 + intercept + condition + presentation + offset(log(secs)) + 
               (0 + intercept + condition | study/ID),
             zi ~ 0 + intercept + condition + presentation + 
               (0 + intercept + condition | study/ID)),
          prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                    prior(normal(0, 1), class = b, coef = "condition"),
                    prior(normal(0, 1), class = b, coef = "presentation"),
                    prior(logistic(0, 1), class = b, coef = "intercept", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "condition", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "presentation", dpar = zi)),
          iter = 2000, warmup = 1000, chains = 4, cores = 4,
          control = list(adapt_delta = 0.995, max_treedepth = 15))

m1.7 <- add_ic(m1.7, ic = c("loo","waic"))

save(m1.7, file = 'models/m1.7.rda')
```

```{r echo=F}
load('models/m1.7.rda')
summary(m1.7)
```

The effect of condition persists when controlling for presentation type (video and audio or audio-only).

```{r}
post <- posterior_samples(m1.7)
sum(post$b_condition > 0) / 4000
```

Bayes factor.

```{r}
(hyp1.7 <- hypothesis(m1.7, "condition > 0"))
```

Model comparison.

```{r}
compare_ic(m1.2, m1.7, ic = "waic")
compare_ic(m1.2, m1.7, ic = "loo")
```

`m1.7` surpasses `m1.2`. This is because presentation type seems to have an effect on yawning rate: dogs seems to yawn less when stimuli are both visual and auditory, rather than only auditory.

## 1.8. Condition + Live model

```{r echo=F, eval=F}
m1.8 <- brm(data = d, family = zero_inflated_poisson,
          bf(numberYawns ~ 0 + intercept + condition + live + offset(log(secs)) + 
               (0 + intercept + condition | study/ID),
             zi ~ 0 + intercept + condition + live + 
               (0 + intercept + condition | study/ID)),
          prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                    prior(normal(0, 1), class = b, coef = "condition"),
                    prior(normal(0, 1), class = b, coef = "live"),
                    prior(logistic(0, 1), class = b, coef = "intercept", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "condition", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "live", dpar = zi)),
          iter = 2000, warmup = 1000, chains = 4, cores = 4,
          control = list(adapt_delta = 0.995, max_treedepth = 15))

m1.8 <- add_ic(m1.8, ic = c("loo","waic"))

save(m1.8, file = 'models/m1.8.rda')
```

```{r echo=F}
load('models/m1.8.rda')
summary(m1.8)
```

The effect of condition persists when controlling for whether the demonstration was live or recorded.

```{r}
post <- posterior_samples(m1.8)
sum(post$b_condition > 0) / 4000
```

Bayes factor.

```{r}
(hyp1.8 <- hypothesis(m1.8, "condition > 0"))
```

Model comparison.

```{r}
compare_ic(m1.2, m1.8, ic = "waic")
compare_ic(m1.2, m1.8, ic = "loo")
```

## 1.9. Condition + Demonstrator model

```{r echo=F, eval=F}
m1.9 <- brm(data = d, family = zero_inflated_poisson,
          bf(numberYawns ~ 0 + intercept + condition + demonstrator + offset(log(secs)) + 
               (0 + intercept + condition | study/ID),
             zi ~ 0 + intercept + condition + demonstrator + 
               (0 + intercept + condition | study/ID)),
          prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                    prior(normal(0, 1), class = b, coef = "condition"),
                    prior(normal(0, 1), class = b, coef = "demonstrator"),
                    prior(logistic(0, 1), class = b, coef = "intercept", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "condition", dpar = zi),
                    prior(normal(0, 1), class = b, coef = "demonstrator", dpar = zi)),
          iter = 2000, warmup = 1000, chains = 4, cores = 4,
          control = list(adapt_delta = 0.995, max_treedepth = 15))

m1.9 <- add_ic(m1.9, ic = c("loo","waic"))

save(m1.9, file = 'models/m1.9.rda')
```

```{r echo=F}
load('models/m1.9.rda')
summary(m1.9)
```

The effect of condition persists.

```{r}
post <- posterior_samples(m1.9)
sum(post$b_condition > 0) / 4000
```

Bayes factor.

```{r}
(hyp1.9 <- hypothesis(m1.9, "condition > 0"))
```

Model comparison.

```{r}
compare_ic(m1.2, m1.9, ic = "waic")
compare_ic(m1.2, m1.9, ic = "loo")
```

## 1.10. Full model

```{r echo=F, eval=F}
m1.10 <- brm(data = d, family = zero_inflated_poisson,
             bf(numberYawns ~ 0 + intercept + condition + presentation + type + 
                  demonstrator + familiar + live + offset(log(secs)) + 
                  (0 + intercept + condition | study/ID),
                zi ~ 0 + intercept + condition + presentation + type + 
                  demonstrator + familiar + live +
                  (0 + intercept + condition | study/ID)),
             prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                       prior(normal(0, 1), class = b, coef = "condition"),
                       prior(normal(0, 1), class = b, coef = "presentation"),
                       prior(normal(0, 1), class = b, coef = "type"),
                       prior(normal(0, 1), class = b, coef = "demonstrator"),
                       prior(normal(0, 1), class = b, coef = "familiar"),
                       prior(normal(0, 1), class = b, coef = "live"),
                       prior(logistic(0, 1), class = b, coef = "intercept", dpar = zi),
                       prior(normal(0, 1), class = b, coef = "condition", dpar = zi),
                       prior(normal(0, 1), class = b, coef = "presentation", dpar = zi),
                       prior(normal(0, 1), class = b, coef = "type", dpar = zi),
                       prior(normal(0, 1), class = b, coef = "demonstrator", dpar = zi),
                       prior(normal(0, 1), class = b, coef = "familiar", dpar = zi),
                       prior(normal(0, 1), class = b, coef = "live", dpar = zi)),
             iter = 2000, warmup = 1000, chains = 4, cores = 4,
             control = list(adapt_delta = 0.999, max_treedepth = 15))

m1.10 <- add_ic(m1.10, ic = c("loo","waic"))

save(m1.10, file = 'models/m1.10.rda')
```

```{r echo=F}
load('models/m1.10.rda')
summary(m1.10)
```

```{r}
post <- posterior_samples(m1.10)
sum(post$b_condition > 0) / 4000
```

Bayes factor.

```{r}
(hyp1.10 <- hypothesis(m1.10, "condition > 0"))
```

Model comparison.

```{r}
compare_ic(m1.2, m1.6, m1.7, m1.8, m1.9, m1.10, ic = "waic")
compare_ic(m1.2, m1.6, m1.7, m1.8, m1.9, m1.10, ic = "loo")
```

## 1.11. Plot condition parameter with controls

```{r message=F, warning=F, echo=F}
fig3 <-
  tibble(
    `Condition`                = (exp(posterior_samples(m1.2)$b_intercept + posterior_samples(m1.2)$b_condition) - exp(posterior_samples(m1.2)$b_intercept))*60,
    `Condition + Type`         = (exp(posterior_samples(m1.6)$b_intercept + posterior_samples(m1.6)$b_condition) - exp(posterior_samples(m1.2)$b_intercept))*60,
    `Condition + Presentation` = (exp(posterior_samples(m1.7)$b_intercept + posterior_samples(m1.7)$b_condition) - exp(posterior_samples(m1.2)$b_intercept))*60,
    `Condition + Live`         = (exp(posterior_samples(m1.8)$b_intercept + posterior_samples(m1.8)$b_condition) - exp(posterior_samples(m1.2)$b_intercept))*60,
    `Condition + Demonstrator` = (exp(posterior_samples(m1.9)$b_intercept + posterior_samples(m1.9)$b_condition) - exp(posterior_samples(m1.2)$b_intercept))*60,
    `Full model`               = (exp(posterior_samples(m1.10)$b_intercept + posterior_samples(m1.10)$b_condition) - exp(posterior_samples(m1.10)$b_intercept))*60
  ) %>%
  gather(model, samples) %>%
  
  ggplot(aes(x = samples, y = fct_rev(model))) +
  geom_density_ridges2(fill = "grey90") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  annotate("text", x = 0.75, y = seq(1.4,6.4,by=1), label = c("94%","95%","95%","96%","96%","95%")) +
  annotate("text", x = 0.75, y = 7, label = "Prob mass above zero") +
  xlim(c(-0.25,1.25)) +
  xlab("Difference in yawning rate (per min) between conditions") +
  coord_cartesian(clip = "off") +
  theme_classic() +
  theme(axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.title.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 10)))

ggsave(fig3, file = "figures/fig3.pdf", width = 8, height = 4.5)

fig3
```

# 2. Fit Poisson models

## 2.1. Intercept-only model

We remove the assumption of zero-inflation and fit an intercept-only Poisson model.

```{r echo=F, eval=F}
m2.1 <- brm(data = d, family = poisson,
            numberYawns ~ 1 + offset(log(secs)) + (1 | study/ID),
            iter = 2000, warmup = 1000, chains = 4, cores = 4,
            control = list(adapt_delta = 0.99))

m2.1 <- add_ic(m2.1, ic = c("loo","waic"))

save(m2.1, file = 'models/m2.1.rda')
```

```{r echo=F}
load('models/m2.1.rda')
summary(m2.1)
```

```{r}
post <- posterior_samples(m2.1)

(exp(post$b_Intercept) * 60) %>% # yawns per minute
  median() %>%
  round(2)
```

The dogs yawn 0.09 times a minute, on average. Predictably, this is less than estimated by the zero-inflated model.

Model comparison?

```{r}
compare_ic(m1.1, m2.1)
```

The zero-inflated model is superior.

## 2.2. Condition-only model

```{r echo=F, eval=F}
m2.2 <- brm(data = d, family = poisson,
            numberYawns ~ 0 + intercept + condition + offset(log(secs)) + 
              (0 + intercept + condition | study/ID),
            prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                      prior(normal(0, 1), class = b, coef = "condition")),
            iter = 2000, warmup = 1000, chains = 4, cores = 4,
            control = list(adapt_delta = 0.99, max_treedepth = 15))

m2.2 <- add_ic(m2.2, ic = c("loo","waic"))

save(m2.2, file = 'models/m2.2.rda')
```

```{r echo=F}
load('models/m2.2.rda')
summary(m2.2)
```

Get difference between conditions.

```{r}
post <- posterior_samples(m2.2)

# yawning rates (per minute)
cond1 <- exp(post$b_intercept) * 60
median(cond1)

cond2 <- exp(post$b_intercept + post$b_condition) * 60
median(cond2)

diff <- cond2 - cond1

# proportion of prob mass above zero
sum(diff > 0) / 4000
```

Bayes factor for condition parameter.

```{r}
(hyp2.2 <- hypothesis(m2.2, "condition > 0"))
```

The effect of condition is reduced in the Poisson model.

Model comparison?

```{r}
compare_ic(m1.2, m2.2)
```

Again, this model is worse than its zero-inflated counterpart. For this reason, it's probably not worth re-running all the previous zero-inflated models as standard Poisson models.

# Session Info

```{r}
sessionInfo()
```