---
title: "Contagious Yawning in Dogs: Prosocial Experiment Analysis (Part 2)"
author: Scott Claessens and Patrick Neilands
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
    toc: true
    number_sections: false
    toc_float: true
---

The purpose of this document is to analyse data from a new experiment on contagious yawning in dogs in the presence of either a prosocial or antisocial demonstrator.

# 0. Setup

```{r echo=FALSE, cache=FALSE, include=FALSE}
options(width = 120)

library(tidyverse)
library(brms)
library(tidybayes)
library(bayesplot)
library(cowplot)
```

Load the data.

```{r}
d <-
  read.csv("data/yawnProsocial.csv") %>%
  as_tibble() %>%
  # create dummy variables for analysis
  mutate(condition = ifelse(condition == "Anti-Social", 0, 1),
         trial     = ifelse(trial == 1, 0, 1))

d
```

In the previous document (`yawnProsocial.rmd`), we analysed these data using zero-inflated Poisson models. Following the suggestions of two reviewers, we now re-analyse these data using hurdle Poisson models. 

# 1. Fit hurdle Poisson models

## 1.1. Intercept-only model

We fitted this model in the previous document.

```{r echo=F}
load('models/m9.1.rda')
summary(m9.1)
```

What priors did we use?

```{r echo=F}
prior_summary(m9.1)
```

Let's interpret each parameter in turn. The hurdle parameter `hu` is -0.28. This is on the logit scale, so we need to calculate the inverse logit.

```{r}
post <- posterior_samples(m9.1)

1 - inv_logit_scaled(post$b_hu_intercept) %>% # prob of yawning
  median() %>%
  round(2)
```

Let's calculate the average yawning rate.

```{r}
(exp(post$b_intercept) * 60) %>% # Yawning rate (per min)
  median() %>%
  round(2)
```

The dogs yawn 0.17 times a minute, on average.

```{r echo=F}
# cleanup
rm(post)
```

## 1.2. Condition-only model

We also fitted this model in the previous document.

```{r echo=F}
load('models/m9.2.rda')
summary(m9.2)
```

What priors did we use?

```{r echo=F}
prior_summary(m9.2)
```

The condition parameters have 95% CIs crossing zero, suggesting that there is no difference in probability of yawning or yawning rates between conditions. Let's calculate this directly.

```{r}
post <- posterior_samples(m9.2)

# prob yawning in Anti-Social condition
(1 - inv_logit_scaled(post$b_hu_intercept)) %>%
  median() %>%
  round(2)

# prob yawning in Pro-Social condition
(1 - inv_logit_scaled(post$b_hu_intercept + post$b_hu_condition)) %>%
  median() %>%
  round(2)
```

No difference between these probabilities.

```{r}
(sum(post$b_hu_condition > 0) / length(post$b_hu_condition)) %>% round(2)
```

```{r}
# Yawning rate (per min) in Anti-Social condition
(exp(post$b_intercept) * 60) %>%
  median() %>%
  round(2)

# Yawning rate (per min) in Pro-Social condition
(exp(post$b_intercept + post$b_condition) * 60) %>%
  median() %>%
  round(2)
```

Psoterior probability mass shows that the difference between these is not substantial.

```{r}
(sum(post$b_condition < 0) / length(post$b_condition)) %>% round(2)
```

Let's visualise these diferences on the original scales.

```{r echo=F, warning=F, message=F}
figS6_inset <-
  tibble(
    diff  = (1- inv_logit_scaled(post$b_hu_intercept)) - (1 - inv_logit_scaled(post$b_hu_intercept + post$b_hu_condition))
    ) %>%
  ggplot(aes(x = diff)) +
  geom_density(fill = "grey90") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  xlab("difference") +
  xlim(c(-0.6,0.6)) +
  theme_classic() +
  theme(axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 9))

figS6 <-
  tibble(
    Antisocial = 1- inv_logit_scaled(post$b_hu_intercept),
    Prosocial  = 1 - inv_logit_scaled(post$b_hu_intercept + post$b_hu_condition)
    ) %>%
  gather(Condition, yawns) %>%
  
  ggplot(aes(x = yawns, fill = Condition, colour = Condition)) +
  geom_density(alpha = 0.1) +
  xlab("Probability of yawning") +
  xlim(c(0, 1)) +
  theme_classic() +
  theme(axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 10)),
        legend.title = element_blank()) +
  annotation_custom(ggplotGrob(figS6_inset), xmin = 0, xmax = 0.3,
                    ymin = 2, ymax = 4.5)

figS6

# save
ggsave(file = "figures/figS6.pdf", figS6, height = 3, width = 6)
ggsave(file = "figures/figS6.jpg", figS6, height = 3, width = 6)
```

```{r echo=F, warning=F, message=F}
fig4a_inset <-
  tibble(
    diff  = (exp(post$b_intercept) - exp(post$b_intercept + post$b_condition)) * 60
    ) %>%
  ggplot(aes(x = diff)) +
  geom_density(fill = "grey90") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  xlab("difference") +
  xlim(c(-0.25,0.5)) +
  theme_classic() +
  theme(axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 9))

fig4a <-
  tibble(
    Antisocial = exp(post$b_intercept) * 60,
    Prosocial  = exp(post$b_intercept + post$b_condition) * 60
    ) %>%
  gather(Condition, yawns) %>%
  
  ggplot(aes(x = yawns, fill = Condition, colour = Condition)) +
  geom_density(alpha = 0.1) +
  xlab("Yawning rate (per min)") +
  xlim(c(0, 0.6)) +
  theme_classic() +
  theme(axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 10)),
        legend.title = element_blank()) +
  annotation_custom(ggplotGrob(fig4a_inset), xmin = 0.35, xmax = 0.6,
                    ymin = 3.5, ymax = 8)

fig4a
```

```{r echo=F}
# cleanup
rm(fig4a_inset, figS6_inset, post)
```

## 1.3. Trial-only model

```{r eval=F, echo=F}
m9.3 <- brm(data = d, family = hurdle_poisson,
            bf(numberYawns ~ 0 + intercept + trial + offset(log(secs)) + 
                 (0 + intercept + trial | ID),
               hu ~ 0 + intercept + trial + 
                 (0 + intercept + trial | ID)),
            prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                      prior(normal(0, 1), class = b, coef = "trial"),
                      prior(logistic(0, 1), class = b, coef = "intercept", dpar = hu),
                      prior(normal(0, 1), class = b, coef = "trial", dpar = hu),
                      prior(student_t(3, 0, 0.5), class = sd, dpar = hu)),
            iter = 2000, warmup = 1000, chains = 4, cores = 4,
            control = list(adapt_delta = 0.999, max_treedepth = 15))

m9.3 <- add_criterion(m9.3, c("loo","waic"))

save(m9.3, file = 'models/m9.3.rda')
```

```{r echo=F}
load('models/m9.3.rda')
summary(m9.3)
```

Priors.

```{r echo=F}
prior_summary(m9.3)
```

## 1.4. Condition + Trial model

```{r eval=F, echo=F}
m9.4 <- brm(data = d, family = hurdle_poisson,
            bf(numberYawns ~ 0 + intercept + condition + trial + offset(log(secs)) + 
                 (0 + intercept + condition + trial | ID),
               hu ~ 0 + intercept + condition + trial + 
                 (0 + intercept + condition + trial | ID)),
            prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                      prior(normal(0, 1), class = b, coef = "condition"),
                      prior(normal(0, 1), class = b, coef = "trial"),
                      prior(logistic(0, 1), class = b, coef = "intercept", dpar = hu),
                      prior(normal(0, 1), class = b, coef = "condition", dpar = hu),
                      prior(normal(0, 1), class = b, coef = "trial", dpar = hu),
                      prior(student_t(3, 0, 0.5), class = sd, dpar = hu)),
            iter = 2000, warmup = 1000, chains = 4, cores = 4,
            control = list(adapt_delta = 0.999, max_treedepth = 15))

m9.4 <- add_criterion(m9.4, c("loo","waic"))

save(m9.4, file = 'models/m9.4.rda')
```

```{r echo=F}
load('models/m9.4.rda')
summary(m9.4)
```

Priors.

```{r echo=F}
prior_summary(m9.4)
```

## 1.5. Interaction model

```{r eval=F, echo=F}
m9.5 <- brm(data = d, family = hurdle_poisson,
            bf(numberYawns ~ 0 + intercept + condition + trial + condition:trial + offset(log(secs)) + 
                 (0 + intercept + condition + trial + condition:trial | ID),
               hu ~ 0 + intercept + condition + trial + condition:trial + 
                 (0 + intercept + condition + trial + condition:trial | ID)),
            prior = c(prior(student_t(3, -2, 10), class = b, coef = "intercept"),
                      prior(normal(0, 1), class = b, coef = "condition"),
                      prior(normal(0, 1), class = b, coef = "trial"),
                      prior(normal(0, 1), class = b, coef = "condition:trial"),
                      prior(logistic(0, 1), class = b, coef = "intercept", dpar = hu),
                      prior(normal(0, 1), class = b, coef = "condition", dpar = hu),
                      prior(normal(0, 1), class = b, coef = "trial", dpar = hu),
                      prior(normal(0, 1), class = b, coef = "condition:trial", dpar = hu),
                      prior(student_t(3, 0, 2), class = sd), # added prior to help estimation
                      prior(student_t(3, 0, 0.5), class = sd, dpar = hu)),
            iter = 2000, warmup = 1000, chains = 4, cores = 4,
            control = list(adapt_delta = 0.999, max_treedepth = 15))

m9.5 <- add_criterion(m9.5, c("waic","loo"))

save(m9.5, file = 'models/m9.5.rda')
```

```{r echo=F}
load('models/m9.5.rda')
summary(m9.5)
```

What priors did we use?

```{r echo=F}
prior_summary(m9.5)
```

Are there any differences between cells in the 2x2 design? Start with probability.

```{r}
post <- posterior_samples(m9.5)

# prob yawning
anti1prob <- 1 - inv_logit_scaled(post$b_hu_intercept)
anti2prob <- 1 - inv_logit_scaled(post$b_hu_intercept + post$b_hu_trial)
pro1prob  <- 1 - inv_logit_scaled(post$b_hu_intercept + post$b_hu_condition)
pro2prob  <- 1 - inv_logit_scaled(post$b_hu_intercept + post$b_hu_condition + post$b_hu_trial + post$`b_hu_condition:trial`)

# differences
diff1 <- anti1prob - anti2prob
diff2 <- anti1prob - pro1prob
diff3 <- anti1prob - pro2prob
diff4 <- anti2prob - pro1prob
diff5 <- anti2prob - pro2prob
diff6 <- pro1prob  - pro2prob

(sum(diff1 < 0) / length(diff1)) %>% round(2)
(sum(diff2 < 0) / length(diff2)) %>% round(2)
(sum(diff3 < 0) / length(diff3)) %>% round(2)
(sum(diff4 < 0) / length(diff4)) %>% round(2)
(sum(diff5 < 0) / length(diff5)) %>% round(2)
(sum(diff6 < 0) / length(diff6)) %>% round(2)

# interaction
(sum(diff2 - diff5 < 0) / length(diff2)) %>% round(2)
```

No differences between cells or interaction effect.

```{r}
# Yawning rate (per min)
anti1rate <- exp(post$b_intercept) * 60
anti2rate <- exp(post$b_intercept + post$b_trial) * 60
pro1rate  <- exp(post$b_intercept + post$b_condition) * 60
pro2rate  <- exp(post$b_intercept + post$b_condition + post$b_trial + post$`b_condition:trial`) * 60

# differences
diff1 <- anti1rate - anti2rate
diff2 <- anti1rate - pro1rate
diff3 <- anti1rate - pro2rate
diff4 <- anti2rate - pro1rate
diff5 <- anti2rate - pro2rate
diff6 <- pro1rate  - pro2rate

(sum(diff1 > 0) / length(diff1)) %>% round(2)
(sum(diff2 > 0) / length(diff2)) %>% round(2)
(sum(diff3 > 0) / length(diff3)) %>% round(2)
(sum(diff4 > 0) / length(diff4)) %>% round(2)
(sum(diff5 > 0) / length(diff5)) %>% round(2)
(sum(diff6 > 0) / length(diff6)) %>% round(2)

# interaction
(sum(diff2 - diff5 < 0) / length(diff2)) %>% round(2)
```

No substantial differences between cells or interaction effect.

## 1.6. Compare models

```{r}
loo_compare(m9.1, m9.2, m9.3, m9.4, m9.5)
```

```{r echo=F}
# visualise model comparison
fig4b <-
  tibble(
    elpd_diff = c(loo_compare(m9.1, m9.2)[2],
                  loo_compare(m9.1, m9.3)[2],
                  loo_compare(m9.1, m9.4)[2],
                  loo_compare(m9.1, m9.5)[2]),
    se_diff = c(loo_compare(m9.1, m9.2)[4],
                  loo_compare(m9.1, m9.3)[4],
                  loo_compare(m9.1, m9.4)[4],
                  loo_compare(m9.1, m9.5)[4])
        ) %>%
  as.matrix() %>% as_tibble() %>%
  mutate(model = c("Prosocial",
                   "Trial",
                   "Prosocial+Trial",
                   "Prosocial*Trial")) %>%
  
  ggplot(aes(x = fct_rev(factor(model, levels = model)), 
             y = elpd_diff, 
             ymin = elpd_diff - (se_diff*1.96), 
             ymax = elpd_diff + (se_diff*1.96))) +
  geom_pointrange(size = 0.35) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  coord_flip() +
  xlab(NULL) +
  ylim(-8,8) +
  ylab("Difference in expected predictive accuracy\nfrom null model") +
  theme_classic() +
  theme(axis.title.x = element_text(size = 10))

fig4b

# save for publication
fig4 <- plot_grid(fig4a, NULL, fig4b, labels = c("a","","b"), nrow=1,
                  rel_widths = c(1, 0.05, 0.85))
ggsave(file = "figures/fig4.pdf", fig4, height = 3.5, width = 8)
ggsave(file = "figures/fig4.jpg", fig4, height = 3.5, width = 8)
```

```{r echo=F}
# cleanup
rm(fig4a, fig4b, post, anti1prob, anti1rate, anti2prob, anti2rate,
   pro1prob, pro1rate, pro2prob, pro2rate, diff1, diff2, diff3, diff4,
   diff5, diff6)
```

# Session Info

```{r}
sessionInfo()
```